My title

### 2024-04-19 paper/paper.qmd
fixed section references

The data section (@sec-data) explains how the source of the data, how it was collected, how it was cleaned and analyzed, and visualizations of the data. 
The model section (@sec-model) explains the model used to fit the dataset.
The results section (@sec-results) explains the results of the analysis with visualizations.

@@

# Model
## Model set-up

@@

### Model justification

@@

# Results
@fig-kdr-wr shows the relationship between K/D and map win rates with a line provided by the linear regression model.
The overall relationships in this figure and following figures are difficult to see using only data points due to the number and distribution.
However, the regression line suggests there is a positive correlation between K/D and win rate, as expected when constructing the model.

@@

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

>>>>

@sec-data explains the source of the data, how it was collected, how it was cleaned and analyzed, and visualizations of the data. 
@sec-model presents the model used to fit the dataset, the predictors used, and a justification for the model.
@sec-results explains the results of the analysis with visualizations.
@sec-discussion provides discussion on the results of this paper as well as weaknesses and next steps.

@@

# Model {#sec-model}
## Model set-up

@@

## Model justification

@@

# Results {#sec-results}
@fig-kdr-wr shows the relationship between K/D and map win rates with a line provided by the linear regression model.
The overall relationships in this figure and following figures are difficult to see using only data points due to the number and distribution.
However, the regression line suggests there is a positive correlation between K/D and win rate, as expected when constructing the model.

@@

# Discussion{#sec-discussion}

## Impacts of an individual on team performance
